The Importance of Initial Conditions in Seasonal Predictions of Antarctic Sea Ice

### 2025-11-19 analysis/paper/access-ice.qmd
Adds competing intests and author contributions

The underlying code for this study is available on GitHub and can be accessed via this link https://github.com/eliocamp/access-s2_ice-eval.

Raw data of +S1 and +S2 forecasts are not available due to size. 
Derived datasets required to reproduce the results are available in this Zenodo repository: https://zenodo.org/records/17479538 [@campitelli2025]

>>>>

The underlying code for this study is available on GitHub: https://github.com/eliocamp/access-s2_ice-eval.

Raw data of +S1 and +S2 hindcast are not available due to size. 
Derived datasets required to reproduce the results, including extent timeseries and error measures, are available in this Zenodo repository: https://zenodo.org/records/17479538 [@campitelli2025]

# Competing interests

All authors declare no financial or non-financial competing interests.

# Author contributions

EC performed the data analysis and wrote the manuscript draft. 
AP, JA, EL, MW and PR, performed interpretation of the results, and reviewed and edited the draft. 
All authors read and approved the final manuscript.
